The \dealii Library, Version 9.6

### 2024-08-19 9.6/paper.tex
Write on libCEED

>>>>

Furthermore, we added an example to the \texttt{libCEED}
library\footnote{\url{https://github.com/CEED/libCEED}}. \texttt{libCEED} is a library
that provides matrix-free evaluation routines that work on different hardware. The
examples show how to interface the \dealii data structures to the \texttt{libCEED} ones.
The BP1-BP6 benchmarks (scalar/vector Laplace/mass matrix are solved with
regular integration and over-integration) are solved.
